\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-07 doc/sw-system.tex
Fixed #197 by changing tile size from 84 to 82 arcsec throughout

We describe \SW, a novel gravitational lens discovery service that yields
samples of high purity and completeness through crowd-sourced visual inspection.
Carefully produced colour composite images are displayed to volunteers via a
web-based classification interface, which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified images which
lack lenses, are inserted into the image stream at random intervals; this
training set is used to give the volunteers feedback on their performance, as
well as to calibrate a model of the system that provides
dynamical updates to the probability of containing a lens
of every image they classify. Low probability systems are
retired from the site periodically, concentrating the sample towards a set of
candidates. Having divided 160 square degrees of Canada-France-Hawaii Telescope
Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 84 by 84 arcsecond
tiles and displaying them on the site, we were joined by around 37,000
volunteers who contributed 11~million image classifications over the course of 8
months. The sample was reduced to 3368 \StageOne candidates; these were then
refined to yield a sample that we expect to be over 90\% complete and 30\% pure.
We comment on the scalability of the \SW system to the wide field survey era,
based on our finding that searches of $10^5$ images can be performed by a
crowd of $10^5$ volunteers in 6 days.
\end{abstract}

@@

In order to investigate the completeness of the previous, semi-automated, lens
searches in the \cfhtls area, we designed a ``blind search.'' We divided the
\cfhtls pointings into some 430,000 equal size, overlapping tiles, approximately
84~arcsec on a side. We refer to these images as ``test images.'' The ``training
images'' were derived from a small subset of these, as  discussed above. In
future, larger area, projects we expect to implement a somewhat different
strategy of producing image tiles centred on particular pre-selected
``targets,'' which might make for a more efficient (if less complete) survey.
However, we do not expect the performance of citizen image inspectors to change
significantly between these strategies: to first order, both strategies require
the inspectors to learn what lenses look like, and then search the presented
images for similar features.

>>>>

We describe \SW, a novel gravitational lens discovery service that yields
samples of high purity and completeness through crowd-sourced visual inspection.
Carefully produced colour composite images are displayed to volunteers via a
web-based classification interface, which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified images which
lack lenses, are inserted into the image stream at random intervals; this
training set is used to give the volunteers feedback on their performance, as
well as to calibrate a model of the system that provides
dynamical updates to the probability of containing a lens
of every image they classify. Low probability systems are
retired from the site periodically, concentrating the sample towards a set of
candidates. Having divided 160 square degrees of Canada-France-Hawaii Telescope
Legacy Survey (\cfhtls) imaging into some 430,000 overlapping 82 by 82 arcsecond
tiles and displaying them on the site, we were joined by around 37,000
volunteers who contributed 11~million image classifications over the course of 8
months. The sample was reduced to 3368 \StageOne candidates; these were then
refined to yield a sample that we expect to be over 90\% complete and 30\% pure.
We comment on the scalability of the \SW system to the wide field survey era,
based on our finding that searches of $10^5$ images can be performed by a
crowd of $10^5$ volunteers in 6 days.
\end{abstract}

@@

In order to investigate the completeness of the previous, semi-automated, lens
searches in the \cfhtls area, we designed a ``blind search.'' We divided the
\cfhtls pointings into some 430,000 equal size, overlapping tiles, approximately
82~arcsec on a side. We refer to these images as ``test images.'' The ``training
images'' were derived from a small subset of these, as  discussed above. In
future, larger area, projects we expect to implement a somewhat different
strategy of producing image tiles centred on particular pre-selected
``targets,'' which might make for a more efficient (if less complete) survey.
However, we do not expect the performance of citizen image inspectors to change
significantly between these strategies: to first order, both strategies require
the inspectors to learn what lenses look like, and then search the presented
images for similar features.
